\section{Conclusions}

This work described the design of 
a high-speed digital signal processing system for nuclear fusion pulses
based on Field Programmable Gate Arrays.
Considerations and test results regarding real-time pulse detection, processing, 
multi-threaded acquisition systems and data transfer and archiving were presented.


The state-of-the-art analysis conducted by the author allowed for the identification
and selection of pulse processing algorithms most suitable for real time digital spectroscopy.
The filters were first compared in research literature
and then implemented in simulations created in Matlab and Python.
Simulations were ran with different 
configurations to find the best algorithm to use in plasma diagnostics. With this
information the designs were implemented in a Field Programmable Gate Array
and interfaced with an Analog to Digital Converter sampling with a gigasample frequency.
The FPGA tests were run with a real radioactive $^{137} Cs$ sample.


While some digital filters perform substantially better than others
they were found to come with different drawbacks. 
Fine-tuned algorithms like the trapezoidal filter
offer better accuracy than simple methods like the boxcar. The cost of this
increased accuracy is usually higher system complexity and lesser universality. 
Reduction of pile-up effects is one of the most important features of 
both detection and shaping algorithms.


Field Programmable Gate Arrays offer advantages over both 
ASICs and CPUs. In digital signal processing they offer greater parallelism and lower latency
than CPUs, and much better reconfigurability when compared to ASICs. 
This makes them a perfect choice for highly experimental systems, like tokamaks.
With FPGAs changes to filters and algorithms can be introduced remotely and
can involve near complete rewrites of the underlying firmware.
On the other hand, although the devices allow for great performance gains, 
they often require complex algorithm pipelining in implementation. 
Additionally, the typical development time is longer than with CPUs.


Maintaining a high data throughput in digital signal processing systems
is a complicated task, that requires high optimization at multiple levels.
Internal buffers of the digitizer must be regularly transferred to the host PC.
The host PC must be capable of processing them at speeds comparable to their appearance.
This requires the use of multiprocessing.
Threaded applications come with a much greater amount of risk
and require a lot of optimization and debugging
when it comes to their routines and synchronization mechanisms.
Any software, hardware or firmware bottlenecks cause buffers to fill, 
which in turn greatly increase the likelihood of data loss.

\subsection{Further problems and research}

Despite a successful implementation of the system at hand, 
many problems that a similar setup will have to face
if used at ITER remain yet to be solved.
Pile-ups still pose a significant threat to the currently used processing algorithms. 
Some prototypes for rejection
were developed but their performance was not yet properly tested in firmware
due to time and resource constraints of this work.


The tests done on the constructed HXRM setup described here
involved only well-formed exponential pulses.
In ITER, the light attenuation from the fiber optic interface
will cause the pulse shapes to divert from exponential curves.
It is possible, that entirely different detection and shaping
algorithms will have to be developed to account for the high 
attenuation in the optical path between the scintillator ant the PMT. 


Apart from the functional upgrades, other minor system improvements are planned
in the near future. The critical section of the processing threads
is still in the process of being optimized. The UI is currently 
being reworked to provide a more intuitive experience. 
Some changes are planned to the firmware user registers, to produce
a more universal and easier to configure interface.
The system must also by synchronized with ITER's timestamping 
and triggering system relying on the IEEE 1588 protocol.


